
#Data

Data used in the Northern and Southern yellowtail rockfish assessments are summarized in Figures \ref{fig:data_plot} and \ref{fig:data_plot}.

Data sources for the two models are largely distinct.  Northern fisheries and surveys had very sparse data (if any) for the south and vice-versa.  Among the 12 data sources referenced below, only 2 data sources are common to both models.  These are the MRFSS/RecFIN recreational dockside survey, which focuses on California and Oregon, and the CalCOM California commercial dataset, which contributed data from the northern-most California counties (Eureka and Del Norte) to the Northern model.  The CalCOM data account for less than five percent of the commercial landings in the Northern model, and less than 1% of the biological samples. 

Commercial landings are not differentiated in either model.  For the Northern model, this is due to the very small portion (1.15 %) of the landings that are attributed to non-trawl gear.  For the Southern model, this is due to the paucity of data.

A description of each model's data sources follows.

<!-- ************FISHERY-DEPENDENT DATA************************************ -->


##Northern Model Data

###Commercial Fishery Landings

**Washington Catch Information**   
The Washington Department of Fisheries and Wildlife (WDFW) provided historical yellowtail catch for 1889–1980.  Landings for 1981-2016 came from the Pacific Fisheries Information Network (PacFIN) database.  WDFW also provided catches for the period 1981 – 2016 to include the re-distribution of the unspeciated "URCK" landings in PacFIN; this information is currently not available from PacFIN.  

**Oregon Catch Information**   
The Oregon Department of Fisheries and Wildlife (ODFW) provided historical yellowtail catch from 1892-1985.  ODFW also provided estimates of yellowtail rockfish in the in the un-speciated PacFIN "URCK" and "POP1" catch categories for recent years, and those estimates were combined with PacFIN landings for 1986-2016.

**Northern California Catch**   
The California Commercial Fishery Database (CalCOM) provided landings for the Northern model for the two counties north of 40.10 (Eureka and Del Norte) for 1969-2016.

**Hake Bycatch**   
The Alaska Fisheries Science Center (AFSC) provided data for yellowtail bycatch in the hake fishery from 1976-2016.

###Sport Fishery Removals

**Washington Sport Catch**   
WDFW provided recreational catches for 1967 and 1975-2016.

**Oregon Sport Catch**   
ODFW provided recreational catch data for 1979-2016.

###Estimated Discards

**Commercial Discards**   
The West Coast Groundfish Observing Program (WCGOP) is an onboard observer program that has extensively surveyed fishing practices since 2002, with nearly 100% observer coverage in the trawl sector in recent years.  WCGOP provided discard ratios for yellowtail rockfish from 2002 to 2015.

**Pikitch Study**  
The Pikitch study was conducted between 1985 and 1987 [@Pikitch1988].  The northern 
and southern boundaries of the study were $48^\circ 42^\prime$ N latitude and 
$42^\circ 60^\prime$ N. latitude respectively, which is primarily within the 
Columbia INPFC area [@Pikitch1988 ; @Rogers1992].  

Participation in the study 
was voluntary and included vessels using bottom, midwater, and shrimp trawl gears.  
Observers of normal fishing operations on commercial vessels collected the data, 
estimated the total weight of the catch by tow and recorded the weight of species 
retained and discarded in the sample.  
 
Pikitch study discards were aggregated due to small sample size and included in the
data as representing a single year mid-way through the study.

###Abundance Indices

**Commercial Logbook CPUE**   
The commercial logbook (fish-ticket) data in PacFIN was used to generate an index for the years 1987-1998, a period in which management of the fishery was stable, i.e., regulations weren"t changing fishery practices.

**Hake Bycatch Index**   
The Hake bycatch data provided by AFSC was used to generate an index of abundance for 1985-1999.

**Pikitch Study**  
The Pikitch data referenced above provided an index for years 1981-91.

<!-- ************FISHERY-INDPENDENT DATA*********************************** -->

###Fishery-Independent Data

**Northwest Fisheries Science Center (NWFSC) shelf-slope survey**     
This survey, referred to as the “NWFSCcombo Survey”, has been conducted annually since 2003.  
The survey consistently covers depths between 30 and 700 fm.

Data from this survey for yellowtail rockfish was available for 2003-2016, and provided an index
in addition to length and age data.

**Alaska Fisheries Science Center (AFSC) shelf survey**    
The survey, often referred to as the “Triennial Survey"" was conducted by the AFSC every 
third year between 1977 and 2001, (and was conducted in 2004 by the NWFSC using the 
same protocols).  The Triennial Survey trawled in depths of 30 to 275 fm.

The Triennial Survey provided yellowtail rockfish length and age data, as well as an index of
abundance from 1997-2004.


<!--************BIOLOGICAL DATA*********************************************-->
###Biological Samples

**Length And Age Compositions**   
Length composition data were compiled from PacFIN for Oregon and Washington for the Northern model and combined
with raw (unexpanded) length data from CalCOM for the two California counties north of 40.10 (Eureka and Del Norte counties).


Note that sample-sizes are the number of fish for recreational sources (since "tow" data is missing for most sources, we prefer to let each fish represent itself), and for commercial and survey data model input sample sizes are calculated as:

  SampleSize = Ntows + 0.138 if Nfish/Ntows < 44; Ntows * 7.06 otherwise (Ian Stewart, pers. comm.)
  


Length compositions were provided from the following sources:
<!-- ***********Indices of abundance summary table************************* -->
```{r, results = "asis"}
    Length_sources = read.csv("./txt_files/02_Summary_N_Length_sources.csv")
      colnames(Length_sources) = c("Source",
                                  "Type",
                                  "Lengths",
                                  "Tows",	
                                  "Years")

   # Lengths summary, create table   
     Length_sources.table = xtable(Length_sources, 
                                  caption = c("Summary of the time series of lengths used in the stock assessment."),
                                 label = "tab:Length_sources", digits = 0)    

    # Print index summary table
      print(Length_sources.table, 
            include.rownames=FALSE, 
            caption.placement="top",
            sanitize.text.function = function(x){x})
```
<!-- ---------------------------------------------------------------------- -->

Model input sample-sizes for age data were calculated according to the same algorithm as for lengths, except that the conditional age-at-length sample sizes are the number of fish, regardless of the source of the data.


Age structure data were available from the following sources:
<!-- ***********Indices of abundance summary table************************* -->
```{r, results = "asis"}
    Age_sources = read.csv("./txt_files/02_Summary_N_Age_sources.csv")
      colnames(Age_sources) = c("Source",
                                  "Type",
                                  "Ages",
                                  "Tows",	
                                  "Years")

   # Index of abundance summary, create table   
     Age_sources.table = xtable(Age_sources, 
                                  caption = c("Summary of the
                                              time series of age data used in the stock
                                              assessment."),
                                 label = "tab:Age_sources",
                                 digits = 0)    

    # Print index summary table
      print(Age_sources.table, 
            include.rownames=FALSE, 
            caption.placement="top",
            sanitize.text.function = function(x){x})
```
<!-- ---------------------------------------------------------------------- -->


<!-- ************FISHERY-DEPENDENT DATA************************************ -->


##Southern Model Data

###Commercial Fishery Landings

**California Commercial Landings**   
The California Commercial Fishery Database (CalCOM) provide landings in California south of 40.10 for 1969-2016.

###Sport Fishery Removals

**MRFSS Estimates and RecFIN**  
CDFW provided estimated yellowtail removals for the MRFSS period 1980-1989, 1993-2003.
RecFIN provided landings for 2004-2016.

**Small Research Study**
A small number of fish were collected from the recreational fishery by the Southwest Fisheries Science Center and are included in the data for 1978-1984.

###Estimated Discards

No discard data were available for the Southern model.

###Abundance Indices

**MRFSS Index**  
An index of abundance was developed from trip-aggregated MRFSS data for the years 1980-1989, 1992-2003.

**California Onboard Survey**  
An Onboard recreational survey provided data for an index of abundance provided by the SWFSC for 1987-2016.


<!-- ************FISHERY-INDPENDENT DATA*********************************** -->

###Fishery-Independent Data

**Hook and Line Survey**  
The NWFSC Hook and Line survey provided data for an index in the Southern California Bight from 2004-2016.


<!--************BIOLOGICAL DATA*********************************************-->
###Biological Samples
Length composition samples were available for the Southern model from 5 sources, and ages from 3.


Note that sample-sizes are the number of fish for recreational sources (since "tow" data is missing for most sources, we prefer to let each fish represent itself), and for commercial and survey data model input sample sizes are calculated as:

  SampleSize = Ntows + 0.138 if Nfish/Ntows < 44; Ntows * 7.06 otherwise (Ian Stewart, pers. comm.)
  


Length compositions were provided from the following sources:
<!-- ***********Indices of abundance summary table************************* -->
```{r, results = "asis"}
    Length_sources = read.csv("./txt_files/02_Summary_S_Length_sources.csv")
      colnames(Length_sources) = c("Source",
                                  "Type",
                                  "Lengths",
                                  "Tows",	
                                  "Years")

   # Lengths summary, create table   
     Length_sources.table = xtable(Length_sources, 
                                  caption = c("Summary of the time series of lengths used in the stock assessment."),
                                 label = "tab:Length_sources", digits = 0)    

    # Print index summary table
      print(Length_sources.table, 
            include.rownames=FALSE, 
            caption.placement="top",
            sanitize.text.function = function(x){x})
```
<!-- ---------------------------------------------------------------------- -->

Model input sample-sizes for age data were calculated according to the same algorithm as for lengths, except that the conditional age-at-length sample sizes are the number of fish, regardless of the source of the data.


Age structure data were available from the following sources:
<!-- ***********Indices of abundance summary table************************* -->
```{r, results = "asis"}
    Age_sources = read.csv("./txt_files/02_Summary_S_Age_sources.csv")
      colnames(Age_sources) = c("Source",
                                  "Type",
                                  "Ages",
                                  "Years")

   # Index of abundance summary, create table   
     Age_sources.table = xtable(Age_sources, 
                                  caption = c("Summary of the
                                              time series of age data used in the stock
                                              assessment."),
                                 label = "tab:Age_sources",
                                 digits = 0)    

    # Print index summary table
      print(Age_sources.table, 
            include.rownames=FALSE, 
            caption.placement="top",
            sanitize.text.function = function(x){x})
```
<!-- ---------------------------------------------------------------------- -->



## Biological Parameters Common to Both Models

\vspace{.5cm}
**Aging Precision And Bias**

Age error matrices were developed for double-reads at the PFMC aging lab in Newport, OR and for double reads within the WDFW aging lab.  The Newport lab has done all of the Survey aging for the NWFSC, along with some commercial ages and  the 400 fish from the Small Study.  WDFW provided the bulk of recreational and commercial ages.  Between-lab differences in aging were minute, as were within-lab differences.

\vspace{.5cm}
**Weight-Length**

The weight-length relationship is based on the standard power function: $W = \alpha(L^\beta)$ where $W$ is individual weight (kg), $L$ is length (cm), and $\alpha$ and $\beta$ are coefficients used as constants.

To estimate this relationship, 12,778 samples with both weight and length measurements from the fishery independent surveys were analyzed. These included 6,354 samples from the NWFSC Combo survey, 5,085 from the Triennial survey, and 1,339 from the Hook and Line survey. All Hook and Line survey samples were from the Southern area, along with 910 samples from the other two surveys (Figure \ref{fig:weight-length}). A single weight-length relationship was chosen for females and males in both areas after examining various factors that may influence this relationships, including sex, area, year, and season. None of these factors had a strong influence in the overall results. Season was one of the bigger factors, with fish sampled later in the year showing a small increase in weight at a given length (2-6% depending on the other factors considered). However, season was confounded with area because most of the samples from the Southern area were collected from the Hook and Line survey which takes place later in the year (mid-September to mid-November) and the resolution of other data in the model do not support modeling the stock at a scale finer than a annual time step. Males and females did not show strong differences in either area, and the estimated differences were in opposite directions for the two areas, suggesting that this might be a spurious relationship or confounded with differences timing of the sampling relative to spawning.

The estimated coefficients resulting from this analysis were $\alpha = 1.1843e-05$ and $\beta = 3.0672$.

\vspace{.5cm}
**Maturity And Fecundity**
Maturity was estimated from histological analysis of 

141 samples collected in 2016. These include 96 from the NWFSC Combo survey, 25 from mid-water catches in the NWFSC acoustic/trawl survey, 13 from the Hook and Line survey, and 7 from Oregon Department of Fish and Wildlife. The sample sizes were not adequate to estimate differences in maturity by area. Length at 50\% maturity was estimated at 42.49cm (Figure \ref{fig:maturity.png}) which was consistent with the range 37-45cm cited in the previous assessment [@Wallace2005].


\vspace{.5cm}
**Natural Mortality**

Natural mortality estimates used as priors for the Northern model and as fixed values for the Southern model were provided by Owen Hamel (pers. comm.).


\vspace{.5cm}
**Sex ratios**

The largest fish seen in the data are females, however the oldest are males.  The sex ratio falls off differently in each model, as can be seen in Figs(x,y).

###Environmental Or Ecosystem Data Included In The Assessment

No environmental index is present in either model.





