\captionsetup[table]{labelformat=simple,format=plain,labelsep=period}
<!-- ====================================================================== -->
<!-- ****************************            ****************************** --> 
<!-- ****************************BEGIN TABLES****************************** --> 
<!-- ****************************             ***************************** --> 
<!-- ======================================================================--> 

#Tables

## Northern Model Tables

<!-- ********************************************************************** --> 
<!-- *********************Commercial landings TABLES*********************** --> 
<!-- ********************************************************************** --> 



```{r, results = 'asis'}
    Northern_catch = read.csv('./txt_files/Northern.Catch.csv')
      colnames(Northern_catch) = c('Year',
                                   'Commercial Trawl',
                                   'Hake Bycatch',
                                   'Rec CA and OR',
                                   'Rec WA')

   # Index of abundance summary, create table   
     Northern_catch.table = xtable(Northern_catch, 
                                  caption ='Catch timeseries for the Northern model.',
                                  label = 'tab:Northern_catch',
                                  digits=3)

    addtorow          <- list()
    addtorow$pos      <- list()
    addtorow$pos[[1]] <- c(0)
    addtorow$command  <- c(paste("\\hline \n",
                                 "\\endhead \n",
                                 "\\hline \n",
                                 "\\multicolumn{3}{l}",
                                 "{\\footnotesize Continued on next page} \n",
                                 "\\endfoot \n",
                                 "\\endlastfoot \n",sep=""))



    # Print
    print(Northern_catch.table, 
          include.rownames = FALSE,
          caption.placement = 'top',
          tabular.environment = 'longtable',
          floating = FALSE,
          add.to.row = addtorow)
```

\newpage

<!-- ********************************************************************** --> 
<!-- *******************Commercial Discards TABLES************************* --> 
<!-- ********************************************************************** --> 


```{r, results = 'asis'}
    Northern_discard = read.csv('./txt_files/Northern.Discards.csv')
      colnames(Northern_discard) = c('Year',
                                   'Discard')

   # Index of abundance summary, create table   
     Northern_discard.table = xtable(Northern_discard, 
                                  caption ='Commercial discard timeseries for the Northern model.',
                                  label = 'tab:Northern_discard',
                                  digits=4)

    # Print
    print(Northern_discard.table, 
          include.rownames = FALSE,
          caption.placement = 'top',
          sanitize.text.function = function(x){x})
```
\newpage
<!-- ***********Indices of abundance summary table************************* -->
```{r, results = 'asis'}
    Index_summary = read.csv('./txt_files/Index_summary.csv')
      colnames(Index_summary) = c('Years',	
                                  'Name',
                                  'Fishery ind.',
                                  'Method',	
                                  'Endorsed')

   # Index of abundance summary, create table   
     Index_summary.table = xtable(Index_summary, 
                                  caption = c('Summary of the biomass/abundance
                                              time series used in the stock
                                              assessment.'),
                                 label = 'tab:Index_summary',
                                 digits = 0)    

    # Print index summary table
      print(Index_summary.table, 
            include.rownames=FALSE, 
            caption.placement='top',
            sanitize.text.function = function(x){x})
```
<!-- ---------------------------------------------------------------------- -->

\newpage

<!-- ********************************************************************** --> 
<!-- ************ CPUE Table                     ************************* --> 
<!-- ********************************************************************** --> 


```{r, results = 'asis'}
    Northern_CPUE = read.csv('./txt_files/Northern.CPUE.csv')
      colnames(Northern_CPUE) = c('Year',
                                   'Commercial Trawl',
                                   'SE',
                                   'Hake ByCatch',
                                   'SE',
                                   'NWFSCcombo',
                                   'SE',
                                   'Triennial',
                                   'SE')

   # Index of abundance summary, create table   
     Northern_CPUE.table = xtable(Northern_CPUE, 
                                  caption ='CPUE timeseries for the Northern model.',
                                  label = 'tab:Northern_CPUE',
                                  digits=2)

    # Print
    print(Northern_CPUE.table,
          include.rownames = FALSE,
          caption.placement = 'top',
          sanitize.text.function = function(x){x})
```
\newpage



<!-- ********************************************************************** --> 
<!-- ************Recreational dockside survey TABLES*********************** --> 
<!-- ********************************************************************** --> 



<!-- ********************************************************************** -->
<!-- ************Recreational onboard observer index TABLES**************** -->
<!-- ********************************************************************** -->




<!-- ********************************************************************** -->
<!--  ************Fishery dependent biological sampling TABLES************* -->
<!-- ********************************************************************** -->


<!-- ====================================================================== --> 
<!-- ******************START BIOLOGICAL DATA TABLES************************ --> 
<!-- ====================================================================== --> 




<!-- ********************************************************************** -->
<!-- ***********************Weight-length TABLES*************************** --> 
<!-- ********************************************************************** -->




<!-- ********************************************************************** --> 
<!-- ******************Maturity and Fecundity TABLES*********************** --> 
<!-- ********************************************************************** --> 


<!-- ********************************************************************** -->
<!-- **********************Age Structure TABLES**************************** --> 
<!-- ********************************************************************** -->


<!-- ====================================================================== -->
<!-- ********************BASE-CASE MODEL 1 TABLES************************** --> 
<!-- **REPEAT THIS SECTION AND EDIT AS NEEDED IF YOU HAVE MULTIPLE MODELS** --> 
<!-- ====================================================================== -->



<!-- ***********JITTER TABLE*********************************************** --> 
```{r, results = 'asis'}
    # Replace values in file and read in - values for all models in 1 table  
      jitter = read.csv('./txt_files/JitterTable.csv')  

    # Create model 1 jitter table
    jitter.table = xtable(jitter, 
                          caption = c('Results from 100 jitters from each of 
                                      the three models.'),
                          label = 'tab:jitter')
    
    # Print jitter table (all models)    
    print(jitter.table, 
          include.rownames = FALSE, 
          caption.placement = 'top')
```
<!-- ---------------------------------------------------------------------- -->

\FloatBarrier
<!-- ***********MODEL 1 PARAMETERS***************************************** --> 
\begin{landscape}
```{r, results='asis'}
       # If you use this for more than one model = change mod1 to mod2 or mod3
    mod_params = mod1$parameters[-c(grep('Recr',mod1$parameters$Label),
                                         grep('Impl',mod1$parameters$Label)),
                                      (names(mod1$parameters) %in%
                                         c("Num","Label","Value","Phase","Min",
                                           "Max","Status","Parm_StDev",
                                           "Pr_type","Prior","Pr_SD"))]  

    # Combine bounds into one column
    mod_params$Min = paste('(', mod_params$Min, ', ', mod_params$Max, ')', sep='')
    
    
    # Combine prior info to one column
    #mod_params$Pr_type = gsub('No_prior', 'None', mod_params$Pr_type)
    mod_params$Pr_type = ifelse(mod_params$Pr_type == 'No_prior' , 'None',
                                paste(mod_params$Pr_type,' (', mod_params$Prior, 
                                      ', ', mod_params$Pr_SD, ')', sep = ''))
    
    # Remove the max, prior and prior sd columns
    drops = c('Max', 'Prior', 'Pr_SD')
    mod_params = mod_params[, !(names(mod_params) %in% drops)]
    
    # Add column names
    colnames(mod_params) = c('No.',
                             'Parameter',
                             'Value',
                             'Phase',
                             'Bounds',
                             'Status',
                             'SD',
                             'Prior (Exp.Val, SD) ')

    # Model 1 model parameters
    mod_params.table = xtable(mod_params, 
                              caption=c(paste('List of parameters used in
                                              the base model, including estimated 
                                              values and standard deviations (SD), 
                                              bounds (minimum and maximum), 
                                              estimation phase (negative values indicate
                                              not estimated), status (indicates if 
                                              parameters are near bounds, and prior type
                                              information (mean, SD).'
                                              , sep='')), 
                              label='tab:Model1_params',
                              digits = c(0,0,0,3,0,3,0,3,0))  

    # Add alignment  
    align(mod_params.table) = c('lrlrrcccl')
        # Add alignment  
     # align(mod_params.table) = c('l',
    #                                 '>{\\raggedright}p{.4in}',
    #                                 '>{\\raggedright}p{.8in}',
    #                                 '>{\\centering}p{.3in}',
    #                                 '>{\\centering}p{.3in}',
    #                                 '>{\\centering}p{.4in}',
    #                                 '>{\\centering}p{.4in}', 
    #                                 '>{\\centering}p{.4in}',
    #                                 '>{\\centering}p{.4in}',
    #                                '>{\\centering}p{.5in}',
    #                                 '>{\\centering}p{.5in}')  
 
    # Add "continued on next page"" footnote   
    addtorow          <- list()
    addtorow$pos      <- list()
    addtorow$pos[[1]] <- c(0)
    addtorow$command  <- c(paste("\\hline \n",
                                 "\\endhead \n",
                                 "\\hline \n",
                                 "\\multicolumn{3}{l}",
                                 "{\\footnotesize Continued on next page} \n",
                                 "\\endfoot \n",
                                 "\\endlastfoot \n",sep=""))



    # Print Model 1 parameters
    print(mod_params.table, 
          include.rownames = FALSE,
          caption.placement = 'top',
          tabular.environment = 'longtable',
          floating = FALSE,
          add.to.row = addtorow)
```
\end{landscape}
<!-- ---------------------------------------------------------------------- -->

\newpage
<!-- ***********MODEL 1 SENSITIVITY TABLE(S)******************************* --> 
```{r, results = 'asis'}
    
    # Read in/organize sensitivity file, change column names, caption
    Sens_model1 = read.csv('./txt_files/Sensitivities_model1.csv')
    colnames(Sens_model1) = c('Label', 
                              'Base (Francis weights)', 
                              'Harmonic mean weights',
                              'Drop index', 
                              'Drop ages', 
                              'Down-weight lengths',
                              'Free size Age0', 
                              'Free CV Amin', 
                              'External growth')

    # Create sensitivities table
    Sens_model1.table = xtable(Sens_model1, 
                               caption = c('Sensitivity of the base model 
                                          to dropping or down-weighting data 
                                          sources and alternative assumptions 
                                          about growth.'),
                               label = 'tab:Sensitivity_model1', digits = 2)    
  
    # Add alignment - this uses centered aligment of .6 inches for all columns 2+,
    # You can change this easily to have variable columns width after you know how many
    # colunns your final table has
    align(Sens_model1.table) = c('l','l', rep('>{\\centering}p{.6in}', dim(Sens_model1)[2]-1))
                    #             '>{\\centering}p{.6in}',
                    #             '>{\\centering}p{.5in}',
                    #             '>{\\centering}p{.5in}',
                    #             '>{\\centering}p{.6in}', 
                    #             '>{\\centering}p{.5in}',
                    #             '>{\\centering}p{.6in}',
                    #             '>{\\centering}p{.6in}',
                    #             '>{\\centering}p{.6in}')  

    # Print model 1 sensitivity table
    print(Sens_model1.table, 
          include.rownames = FALSE,             
          caption.placement = 'top',
          floating.environment = 'sidewaystable',
          scalebox = .9)

```
<!-- ---------------------------------------------------------------------- -->


\newpage
<!-- ***********MODEL 1 REFERENCE POINTS TIME SERIES TABLE***************** --> 
```{r}
   
    
    # Total biomass, extract and subset
    Bio_all = mod1$sprseries[, c('Yr', 'Bio_all')]
    Bio_allyrs = subset(Bio_all, Yr > (Dat_start_mod1 - 1) & Yr < (LastYR + 1))

  
  
    # Spawning biomass, extract and subset, and turn into scientific notation
    SpawningB = mod1$derived_quants[grep('SPB', mod1$derived_quants$Label), ]
    SpawningB = SpawningB[c(-1, -2), ]
    SpawningByrs = SpawningB[SpawningB$Label >= paste('SPB_', Dat_start_mod1, sep='') &  
                             SpawningB$Label <= paste('SPB_', LastYR, sep=''), ] 
        
        SpawningB_units = ''
        if(mean(SpawningByrs$Value) > 1000000){
            SpawningB_units <- "million"
            SpawningByrs$Value <- SpawningByrs$Value/1000000
         }

    
    # Depletion, extract, rename and subset
    Depl_years = as.data.frame(seq(Dat_start_mod1, LastYR, 1))
    colnames(Depl_years) = 'Yr'
    Depl_years$Depl = 0
    Depletion = mod1$derived_quants[grep('Bratio', mod1$derived_quants$Label), ]
    Depletionyrs = Depletion[Depletion$Label >= paste0('Bratio_', Dat_start_mod1) &  
                             Depletion$Label <= paste0('Bratio_', LastYR), ]
    
    Depletionyrs$Yr = Depletionyrs$Label1 = substr(Depletionyrs$Label,
                                                     (nchar(Depletionyrs$Label) + 1) - 4, 
                                                      nchar(Depletionyrs$Label))
   # Make sure depletion is numeric and merge ...
   Depletionyrs$Yr = as.numeric(Depletionyrs$Yr)
   Depleteyrs = merge(Depl_years, Depletionyrs, all.x=T, all.y=T, by.x='Yr', by.y='Yr')
   Depleteyrs[is.na(Depleteyrs)] <- 0
   Depleteyrs$total = Depleteyrs$Depl + Depleteyrs$Value
    
   # Recruits, extract and subset
   Recruit = mod1$derived_quants[grep('Recr', mod1$derived_quants$Label), ]
   Recruit = Recruit[c(-1, -2), ]
   Recruityrs = Recruit[Recruit$Label >= paste('Recr_', Dat_start_mod1, sep='') &  
                        Recruit$Label <= paste('Recr_', LastYR, sep=''), ]  
    
    
   # Landings/total catch, extract and subset years
   Landings = mod1$sprseries[ , c('Yr','Dead_Catch_B')]
   Landingsyrs = subset(Landings, Yr > (Dat_start_mod1 - 1) & Yr < (LastYR + 1))
    
  
    
   # Relatvie exploitation rate, extract, subset and merge
   Exploit = mod1$derived_quants[grep('F', mod1$derived_quants$Label), ]
   Exploit = Exploit[c(-1, -2), ]
   Exploityrs = Exploit[Exploit$Label >= paste('F_', Dat_start_mod1, sep = '') &  
                        Exploit$Label <= paste('F_', LastYR, sep = ''), ]  
   Exploityrs$Yr = Exploityrs$Label1 = substr(Exploityrs$Label, 
                                               (nchar(Exploityrs$Label) + 1) - 4,
                                                nchar(Exploityrs$Label))
   Exploityrs$Yr = as.numeric(Exploityrs$Yr)
   Exploited = merge(Depl_years, Exploityrs, all.x=T, all.y=T, by.x='Yr', by.y='Yr')
   Exploited[is.na(Exploited)] <- 0
   Exploited$total = Exploited$Depl + Exploited$Value
    
  # SPR, extract and subset years
  SPR = mod1$sprseries[, c('Yr', 'SPR')]
  SPRyrs = subset(SPR, Yr > (Dat_start_mod1 - 1) & Yr < (LastYR + 1))
  
  
  # Bind all the columns together for the table
  Timeseries = as.data.frame(cbind(seq(Dat_start_mod1, LastYR, 1), 
                                       Bio_allyrs$Bio_all, 
                                       SpawningByrs$Value,
                                       Depleteyrs$total,
                                       Recruityrs$Value, 
                                       Landingsyrs$Dead_Catch_B, 
                                       Exploited$total,
                                       SPRyrs$SPR))

 # Add colulmn names    
 colnames(Timeseries)=c('Yr', 
                        'Total biomass (mt)', 
                        paste0('Spawning biomass', SpawningB_units, ' (mt)'),
                        'Depletion', 
                        'Age-0 recruits', 
                        'Total catch (mt)',
                        'Relative exploitation rate', 
                        'SPR')
 
 # Make year a factor so you don't have a decimal   
 Timeseries$Yr = as.factor(Timeseries$Yr)
    
 # Remove 2015 values for last three columns since year isn't complete
 Timeseries[nrow(Timeseries), c((ncol(Timeseries) - 2):ncol(Timeseries))] <- NA
```

```{r, results='asis'}
    # Create the time series table
    Timeseries.table = xtable(Timeseries, 
                              caption = c('Time-series of population estimates 
                                        from the base-case model.'),
                              label='tab:Timeseries_mod1',
                              digits = c(0,0,0,0,2,0,0,2,2))   

    # Add alignment
    align(Timeseries.table) = c('l',
                                'c',
                                '>{\\centering}p{.6in}',
                                '>{\\centering}p{.6in}',
                                '>{\\centering}p{.6in}',
                                '>{\\centering}p{.6in}',
                                '>{\\centering}p{.8in}',
                                '>{\\centering}p{.8in}',
                                'c')

    # Print timeseries of population estimates table
    print(Timeseries.table, 
          include.rownames = FALSE, 
          caption.placement = 'top',
          tabular.environment = 'longtable', 
          align=TRUE, 
          floating = FALSE, 
          add.to.row = list(pos = list(0), 
          command = '\\hline \\endhead '))
```
<!-- ---------------------------------------------------------------------- -->

\FloatBarrier

<!-- ***********MODEL 1 HARVEST PROJECTIONS TABLE************************** --> 
\newpage
```{r, results = 'asis'}
    # Pull OFL contribution and subset years
    OFLcatch = mod1$derived_quants[grep('OFLCatch', mod1$derived_quants$Label), ]
    OFLcatchyrs = OFLcatch[OFLcatch$Label >= paste('OFLCatch_', Project_firstyr, sep = '') &
                           OFLcatch$Label <= paste('OFLCatch_', Project_lastyr, sep = ''), ]

    # Pull forecasted landings and subset years
    ForecastC = mod1$timeseries[, grepl('Yr|retain[(]B[)]', names(mod1$timeseries))]
    ForecastC$total = rowSums(ForecastC[, -1])
    ForecastCyrs = subset(ForecastC, Yr > (Project_firstyr - 1) & Yr < (Project_lastyr + 1))

    # Pull Age 5+ biomass and subset years
    Age5biomass = mod1$timeseries[, c('Yr', 'Bio_smry')]
    Age5biomassyrs = subset(Age5biomass, Yr > (Project_firstyr - 1) & Yr < (Project_lastyr + 1))


    # Pull spawning biomass and subset years
    SpawningB = mod1$derived_quants[grep('SPB', mod1$derived_quants$Label), ]
    SpawningB = SpawningB[c(-1, -2), ]
    SpawningByrs = SpawningB[SpawningB$Label >= paste('SPB_', Project_firstyr, sep = '') &
                             SpawningB$Label <= paste('SPB_', Project_lastyr, sep = ''), ]

    # Pull depletion and subset years
    Depletion = mod1$derived_quants[grep('Bratio', mod1$derived_quants$Label), ]
    Depletion = Depletion[c(-1, -2), ]
    Depletionyrs = Depletion[Depletion$Label >= paste('Bratio_', Project_firstyr, sep = '') &
                             Depletion$Label <= paste('Bratio_', Project_lastyr, sep = ''), ]

    # Combine the data for the forecast table
    Forecast_mod1 = as.data.frame(cbind(seq(Project_firstyr, Project_lastyr, 1),
                                        OFLcatchyrs$Value,
                                        ForecastCyrs$total,
                                        Age5biomassyrs$Bio_smry,
                                        SpawningByrs$Value,
                                        Depletionyrs$Value))
    # Add column names
    colnames(Forecast_mod1)=c('Yr',
                           'OFL contriubtion (mt)',
                           'ACL landings (mt)',
                           'Age 5+ biomass (mt)',
                           'Spawning Biomass (mt)',
                           'Depletion')

    # Make sure year is a factor, so you don't get decimals
    Forecast_mod1$Yr = as.factor(Forecast_mod1$Yr)

    # Create the forecast table
    Forecast_mod1.table = xtable(Forecast_mod1,
                              caption = c('Projection of potential
                                        OFL, spawning biomass, and depletion for the
                                        base case model.'),
                              label = 'tab:Forecast_mod1', digits = 2)
    # Add alignment
    align(Forecast_mod1.table) = c('l',
                                   'c',
                                   '>{\\centering}p{1in}',
                                   '>{\\centering}p{1in}',
                                   '>{\\centering}p{1in}',
                                   '>{\\centering}p{1in}',
                                   '>{\\centering}p{1in}')

    # Print model 1 forecast table
    print(Forecast_mod1.table,
          include.rownames = FALSE,
          caption.placement = 'top')
```
<!-- ---------------------------------------------------------------------- -->
\FloatBarrier


<!-- ********************************************************************** -->
<!-- ************************ABLES******************************** --> 
<!-- ********************************************************************** -->

\newpage
## Southern Model Tables

<!-- ********************************************************************** --> 
<!-- *********************Commercial landings TABLES*********************** --> 
<!-- ********************************************************************** --> 



```{r, results = 'asis'}
    Southern_catch = read.csv('./txt_files/Southern.Catch.csv')
      colnames(Southern_catch) = c('Year',
                                   'Commercial Catch',
                                   'Recreational Catch')


   # Index of abundance summary, create table   
     Southern_catch.table = xtable(Southern_catch, 
                                  caption ='Catch timeseries for the Southern model.',
                                  label = 'tab:Southern_catch',
                                  digits=3)

    addtorow          <- list()
    addtorow$pos      <- list()
    addtorow$pos[[1]] <- c(0)
    addtorow$command  <- c(paste("\\hline \n",
                                 "\\endhead \n",
                                 "\\hline \n",
                                 "\\multicolumn{3}{l}",
                                 "{\\footnotesize Continued on next page} \n",
                                 "\\endfoot \n",
                                 "\\endlastfoot \n",sep=""))



    # Print
    print(Southern_catch.table, 
          include.rownames = FALSE,
          caption.placement = 'top',
          tabular.environment = 'longtable',
          floating = FALSE,
          add.to.row = addtorow)
```

\newpage


<!-- ***********Indices of abundance summary table************************* -->
```{r, results = 'asis'}
    Index_summary = read.csv('./txt_files/Index_summary_S.csv')
      colnames(Index_summary) = c('Years',	
                                  'Name',
                                  'Fishery ind.',
                                  'Method',	
                                  'Endorsed')

   # Index of abundance summary, create table   
     Index_summary.table = xtable(Index_summary, 
                                  caption = c('Summary of the biomass/abundance
                                              time series used in the stock
                                              assessment.'),
                                 label = 'tab:Index_summary_S',
                                 digits = 0)    

    # Print index summary table
      print(Index_summary.table, 
            include.rownames=FALSE, 
            caption.placement='top',
            sanitize.text.function = function(x){x})
```
<!-- ---------------------------------------------------------------------- -->

\newpage
<!-- ********************************************************************** --> 
<!-- ************ CPUE Table                     ************************* --> 
<!-- ********************************************************************** --> 


```{r, results = 'asis'}
    Southern_CPUE = read.csv('./txt_files/Southern.CPUE.csv')
      colnames(Southern_CPUE) = c('Year',
                                   'Hook and Line',
                                   'SE',
                                   'Recreational',
                                   'SE',
                                   'Onboard',
                                   'SE',
                                   'Juvenile Survey',
                                   'SE')

   # Index of abundance summary, create table   
     Southern_CPUE.table = xtable(Southern_CPUE, 
                                  caption ='CPUE timeseries for the Southern model.',
                                  label = 'tab:Southern_CPUE',
                                  digits=2)

    # Print
    print(Southern_CPUE.table,
          include.rownames = FALSE,
          caption.placement = 'top',
          sanitize.text.function = function(x){x})
```
\newpage

<!-- ***********JITTER TABLE*********************************************** --> 
```{r, results = 'asis'}
    # Replace values in file and read in - values for all models in 1 table  
      jitter = read.csv('./txt_files/JitterTable_S.csv')  

    # Create model 2 jitter table
    jitter.table = xtable(jitter, 
                          caption = c('Results from 100 jitters from each of 
                                      the three models.'),
                          label = 'tab:jitter')
    
    # Print jitter table (all models)    
    print(jitter.table, 
          include.rownames = FALSE, 
          caption.placement = 'top')
```
<!-- ---------------------------------------------------------------------- -->

\FloatBarrier
<!-- ***********Model 2 PARAMETERS***************************************** --> 
\begin{landscape}
```{r, results='asis'}
       # If you use this for more than one model = change mod2 to mod2 or mod3
    mod_params = mod2$parameters[-c(grep('Recr',mod2$parameters$Label),
                                         grep('Impl',mod2$parameters$Label)),
                                      (names(mod2$parameters) %in%
                                         c("Num","Label","Value","Phase","Min",
                                           "Max","Status","Parm_StDev",
                                           "Pr_type","Prior","Pr_SD"))]  

    # Combine bounds into one column
    mod_params$Min = paste('(', mod_params$Min, ', ', mod_params$Max, ')', sep='')
    
    
    # Combine prior info to one column
    #mod_params$Pr_type = gsub('No_prior', 'None', mod_params$Pr_type)
    mod_params$Pr_type = ifelse(mod_params$Pr_type == 'No_prior' , 'None',
                                paste(mod_params$Pr_type,' (', mod_params$Prior, 
                                      ', ', mod_params$Pr_SD, ')', sep = ''))
    
    # Remove the max, prior and prior sd columns
    drops = c('Max', 'Prior', 'Pr_SD')
    mod_params = mod_params[, !(names(mod_params) %in% drops)]
    
    # Add column names
    colnames(mod_params) = c('No.',
                             'Parameter',
                             'Value',
                             'Phase',
                             'Bounds',
                             'Status',
                             'SD',
                             'Prior (Exp.Val, SD) ')

    # Model 2 model parameters
    mod_params.table = xtable(mod_params, 
                              caption=c(paste('List of parameters used in
                                              the base model, including estimated 
                                              values and standard deviations (SD), 
                                              bounds (minimum and maximum), 
                                              estimation phase (negative values indicate
                                              not estimated), status (indicates if 
                                              parameters are near bounds, and prior type
                                              information (mean, SD).'
                                              , sep='')), 
                              label='tab:Model2_params',
                              digits = c(0,0,0,3,0,3,0,3,0))  

    # Add alignment  
    align(mod_params.table) = c('lrlrrcccl')
        # Add alignment  
     # align(mod_params.table) = c('l',
    #                                 '>{\\raggedright}p{.4in}',
    #                                 '>{\\raggedright}p{.8in}',
    #                                 '>{\\centering}p{.3in}',
    #                                 '>{\\centering}p{.3in}',
    #                                 '>{\\centering}p{.4in}',
    #                                 '>{\\centering}p{.4in}', 
    #                                 '>{\\centering}p{.4in}',
    #                                 '>{\\centering}p{.4in}',
    #                                '>{\\centering}p{.5in}',
    #                                 '>{\\centering}p{.5in}')  
 
    # Add "continued on next page"" footnote   
    addtorow          <- list()
    addtorow$pos      <- list()
    addtorow$pos[[1]] <- c(0)
    addtorow$command  <- c(paste("\\hline \n",
                                 "\\endhead \n",
                                 "\\hline \n",
                                 "\\multicolumn{3}{l}",
                                 "{\\footnotesize Continued on next page} \n",
                                 "\\endfoot \n",
                                 "\\endlastfoot \n",sep=""))



    # Print Model 2 parameters
    print(mod_params.table, 
          include.rownames = FALSE,
          caption.placement = 'top',
          tabular.environment = 'longtable',
          floating = FALSE,
          add.to.row = addtorow)
```
\end{landscape}
<!-- ---------------------------------------------------------------------- -->

\newpage
<!-- ***********Model 2 SENSITIVITY TABLE(S)******************************* --> 
```{r, results = 'asis'}
    
    # Read in/organize sensitivity file, change column names, caption
    Sens_model2 = read.csv('./txt_files/Sensitivities_model2.csv')
    colnames(Sens_model2) = c('Label', 
                              'Base (Francis weights)', 
                              'Harmonic mean weights',
                              'Drop index', 
                              'Drop ages', 
                              'Down-weight lengths',
                              'Free size Age0', 
                              'Free CV Amin', 
                              'External growth')

    # Create sensitivities table
    Sens_model2.table = xtable(Sens_model2, 
                               caption = c('Sensitivity of the base model 
                                          to dropping or down-weighting data 
                                          sources and alternative assumptions 
                                          about growth.'),
                               label = 'tab:Sensitivity_model2', digits = 2)    
  
    # Add alignment - this uses centered aligment of .6 inches for all columns 2+,
    # You can change this easily to have variable columns width after you know how many
    # colunns your final table has
    align(Sens_model2.table) = c('l','l', rep('>{\\centering}p{.6in}', dim(Sens_model2)[2]-1))
                    #             '>{\\centering}p{.6in}',
                    #             '>{\\centering}p{.5in}',
                    #             '>{\\centering}p{.5in}',
                    #             '>{\\centering}p{.6in}', 
                    #             '>{\\centering}p{.5in}',
                    #             '>{\\centering}p{.6in}',
                    #             '>{\\centering}p{.6in}',
                    #             '>{\\centering}p{.6in}')  

    # Print model 2 sensitivity table
    print(Sens_model2.table, 
          include.rownames = FALSE,             
          caption.placement = 'top',
          floating.environment = 'sidewaystable',
          scalebox = .9)

```
<!-- ---------------------------------------------------------------------- -->


\newpage
<!-- ***********Model 2 REFERENCE POINTS TIME SERIES TABLE***************** --> 
```{r}
   
    
    # Total biomass, extract and subset
    Bio_all = mod2$sprseries[, c('Yr', 'Bio_all')]
    Bio_allyrs = subset(Bio_all, Yr > (Dat_start_mod2 - 1) & Yr < (LastYR + 1))

  
  
    # Spawning biomass, extract and subset, and turn into scientific notation
    SpawningB = mod2$derived_quants[grep('SPB', mod2$derived_quants$Label), ]
    SpawningB = SpawningB[c(-1, -2), ]
    SpawningByrs = SpawningB[SpawningB$Label >= paste('SPB_', Dat_start_mod2, sep='') &  
                             SpawningB$Label <= paste('SPB_', LastYR, sep=''), ] 
        
        SpawningB_units = ''
        if(mean(SpawningByrs$Value) > 1000000){
            SpawningB_units <- "million"
            SpawningByrs$Value <- SpawningByrs$Value/1000000
         }

    
    # Depletion, extract, rename and subset
    Depl_years = as.data.frame(seq(Dat_start_mod2, LastYR, 1))
    colnames(Depl_years) = 'Yr'
    Depl_years$Depl = 0
    Depletion = mod2$derived_quants[grep('Bratio', mod2$derived_quants$Label), ]
    Depletionyrs = Depletion[Depletion$Label >= paste0('Bratio_', Dat_start_mod2) &  
                             Depletion$Label <= paste0('Bratio_', LastYR), ]
    
    Depletionyrs$Yr = Depletionyrs$Label1 = substr(Depletionyrs$Label,
                                                     (nchar(Depletionyrs$Label) + 1) - 4, 
                                                      nchar(Depletionyrs$Label))
   # Make sure depletion is numeric and merge ...
   Depletionyrs$Yr = as.numeric(Depletionyrs$Yr)
   Depleteyrs = merge(Depl_years, Depletionyrs, all.x=T, all.y=T, by.x='Yr', by.y='Yr')
   Depleteyrs[is.na(Depleteyrs)] <- 0
   Depleteyrs$total = Depleteyrs$Depl + Depleteyrs$Value
    
   # Recruits, extract and subset
   Recruit = mod2$derived_quants[grep('Recr', mod2$derived_quants$Label), ]
   Recruit = Recruit[c(-1, -2), ]
   Recruityrs = Recruit[Recruit$Label >= paste('Recr_', Dat_start_mod2, sep='') &  
                        Recruit$Label <= paste('Recr_', LastYR, sep=''), ]  
    
    
   # Landings/total catch, extract and subset years
   Landings = mod2$sprseries[ , c('Yr','Dead_Catch_B')]
   Landingsyrs = subset(Landings, Yr > (Dat_start_mod2 - 1) & Yr < (LastYR + 1))
    
  
    
   # Relatvie exploitation rate, extract, subset and merge
   Exploit = mod2$derived_quants[grep('F', mod2$derived_quants$Label), ]
   Exploit = Exploit[c(-1, -2), ]
   Exploityrs = Exploit[Exploit$Label >= paste('F_', Dat_start_mod2, sep = '') &  
                        Exploit$Label <= paste('F_', LastYR, sep = ''), ]  
   Exploityrs$Yr = Exploityrs$Label1 = substr(Exploityrs$Label, 
                                               (nchar(Exploityrs$Label) + 1) - 4,
                                                nchar(Exploityrs$Label))
   Exploityrs$Yr = as.numeric(Exploityrs$Yr)
   Exploited = merge(Depl_years, Exploityrs, all.x=T, all.y=T, by.x='Yr', by.y='Yr')
   Exploited[is.na(Exploited)] <- 0
   Exploited$total = Exploited$Depl + Exploited$Value
    
  # SPR, extract and subset years
  SPR = mod2$sprseries[, c('Yr', 'SPR')]
  SPRyrs = subset(SPR, Yr > (Dat_start_mod2 - 1) & Yr < (LastYR + 1))
  
  
  # Bind all the columns together for the table
  Timeseries = as.data.frame(cbind(seq(Dat_start_mod2, LastYR, 1), 
                                       Bio_allyrs$Bio_all, 
                                       SpawningByrs$Value,
                                       Depleteyrs$total,
                                       Recruityrs$Value, 
                                       Landingsyrs$Dead_Catch_B, 
                                       Exploited$total,
                                       SPRyrs$SPR))

 # Add colulmn names    
 colnames(Timeseries)=c('Yr', 
                        'Total biomass (mt)', 
                        paste0('Spawning biomass', SpawningB_units, ' (mt)'),
                        'Depletion', 
                        'Age-0 recruits', 
                        'Total catch (mt)',
                        'Relative exploitation rate', 
                        'SPR')
 
 # Make year a factor so you don't have a decimal   
 Timeseries$Yr = as.factor(Timeseries$Yr)
    
 # Remove 2015 values for last three columns since year isn't complete
 Timeseries[nrow(Timeseries), c((ncol(Timeseries) - 2):ncol(Timeseries))] <- NA
```

```{r, results='asis'}
    # Create the time series table
    Timeseries.table = xtable(Timeseries, 
                              caption = c('Time-series of population estimates 
                                        from the base-case model.'),
                              label='tab:Timeseries_mod2',
                              digits = c(0,0,0,0,2,0,0,2,2))   

    # Add alignment
    align(Timeseries.table) = c('l',
                                'c',
                                '>{\\centering}p{.6in}',
                                '>{\\centering}p{.6in}',
                                '>{\\centering}p{.6in}',
                                '>{\\centering}p{.6in}',
                                '>{\\centering}p{.8in}',
                                '>{\\centering}p{.8in}',
                                'c')

    # Print timeseries of population estimates table
    print(Timeseries.table, 
          include.rownames = FALSE, 
          caption.placement = 'top',
          tabular.environment = 'longtable', 
          align=TRUE, 
          floating = FALSE, 
          add.to.row = list(pos = list(0), 
          command = '\\hline \\endhead '))
```
<!-- ---------------------------------------------------------------------- -->

\FloatBarrier

<!-- ***********Model 2 HARVEST PROJECTIONS TABLE************************** --> 
\newpage
```{r, results = 'asis'}
    # Pull OFL contribution and subset years
    OFLcatch = mod2$derived_quants[grep('OFLCatch', mod2$derived_quants$Label), ]
    OFLcatchyrs = OFLcatch[OFLcatch$Label >= paste('OFLCatch_', Project_firstyr, sep = '') &
                           OFLcatch$Label <= paste('OFLCatch_', Project_lastyr, sep = ''), ]

    # Pull forecasted landings and subset years
    ForecastC = mod2$timeseries[, grepl('Yr|retain[(]B[)]', names(mod2$timeseries))]
    ForecastC$total = rowSums(ForecastC[, -1])
    ForecastCyrs = subset(ForecastC, Yr > (Project_firstyr - 1) & Yr < (Project_lastyr + 1))

    # Pull Age 5+ biomass and subset years
    Age5biomass = mod2$timeseries[, c('Yr', 'Bio_smry')]
    Age5biomassyrs = subset(Age5biomass, Yr > (Project_firstyr - 1) & Yr < (Project_lastyr + 1))


    # Pull spawning biomass and subset years
    SpawningB = mod2$derived_quants[grep('SPB', mod2$derived_quants$Label), ]
    SpawningB = SpawningB[c(-1, -2), ]
    SpawningByrs = SpawningB[SpawningB$Label >= paste('SPB_', Project_firstyr, sep = '') &
                             SpawningB$Label <= paste('SPB_', Project_lastyr, sep = ''), ]

    # Pull depletion and subset years
    Depletion = mod2$derived_quants[grep('Bratio', mod2$derived_quants$Label), ]
    Depletion = Depletion[c(-1, -2), ]
    Depletionyrs = Depletion[Depletion$Label >= paste('Bratio_', Project_firstyr, sep = '') &
                             Depletion$Label <= paste('Bratio_', Project_lastyr, sep = ''), ]

    # Combine the data for the forecast table
    Forecast_mod2 = as.data.frame(cbind(seq(Project_firstyr, Project_lastyr, 1),
                                        OFLcatchyrs$Value,
                                        ForecastCyrs$total,
                                        Age5biomassyrs$Bio_smry,
                                        SpawningByrs$Value,
                                        Depletionyrs$Value))
    # Add column names
    colnames(Forecast_mod2)=c('Yr',
                           'OFL contriubtion (mt)',
                           'ACL landings (mt)',
                           'Age 5+ biomass (mt)',
                           'Spawning Biomass (mt)',
                           'Depletion')

    # Make sure year is a factor, so you don't get decimals
    Forecast_mod2$Yr = as.factor(Forecast_mod2$Yr)

    # Create the forecast table
    Forecast_mod2.table = xtable(Forecast_mod2,
                              caption = c('Projection of potential
                                        OFL, spawning biomass, and depletion for the
                                        base case model.'),
                              label = 'tab:Forecast_mod2', digits = 2)
    # Add alignment
    align(Forecast_mod2.table) = c('l',
                                   'c',
                                   '>{\\centering}p{1in}',
                                   '>{\\centering}p{1in}',
                                   '>{\\centering}p{1in}',
                                   '>{\\centering}p{1in}',
                                   '>{\\centering}p{1in}')

    # Print model 2 forecast table
    print(Forecast_mod2.table,
          include.rownames = FALSE,
          caption.placement = 'top')
```
<!-- ---------------------------------------------------------------------- -->
\FloatBarrier



<!-- ====================================================================== --> 
<!-- *************************          *********************************** --> 
<!-- *************************END TABLES*********************************** --> 
<!-- *************************          *********************************** --> 
<!-- ====================================================================== --> 


