---
title: 'Status of Yellowtail Rockfish (*Sebastes flavidus*) Along the U.S. Pacific Coast in 2017'
author: ''
date: ''
footer: 'July 5 DRAFT with proposed alternative Southern model'
output:
  pdf_document:
    fig_caption: yes
    highlight: haddock
    includes:
      before_body: Titlepage.tex
      in_header: header.tex
    keep_tex: yes
    number_sections: yes
    template: Default_template_modified.tex
    toc: yes
    toc_depth: 4
  html_document:
    toc: yes
  word_document: default
documentclass: article
fontsize: 12pt
geometry: margin=1in
csl: CJFAS.csl
bibliography: BibFile.bib
link-citations: yes
header-includes:
    - \usepackage{caption}
    - \usepackage{grattanCharts}
---
```{r global_options, include=FALSE}
    # set global options for R code chunks: echo=FALSE (don't include source code); 
    # warning=FALSE (suppress R warnings); message=FALSE (suppress R messages)
    # eval = TRUE is default
    knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
    # Read in preamble R code - including required libraries and the SS file(s)
    source('./Rcode/Preamble.R')
 
    # Read in data/manipulations for executive summary tables and figures
    # It may take time to edit this file and get it ready for your assessment
    # Make small changes in this file and then try to compile the document
    # Commit when you have a success!
    source('./Rcode/Exec_summary_figs_tables.R')
```
\setlength{\parskip}{5mm plus1mm minus1mm}
\pagebreak

\pagenumbering{arabic}
<!--\setcounter{page}{1}-->
\renewcommand{\thefigure}{\alph{figure}}
\renewcommand{\thetable}{\alph{table}}


```{r child = "0_Executive_Summary.Rmd"}
```
<!--************RESET FIGURE & TABLE NUMBERS FOR THE DOCUMENT'S MAIN BODY** -->

\newpage
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thetable}{\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}


<!-- How to comment out any section while debugging doc -->
<!--  -->
<!--  ```{r child='SS_file_appendices.rmd'}
``` --> 

```{r child = "1_Introduction.Rmd"}
```
\newpage
```{r child = "2_Data.Rmd"}
```
\newpage
```{r child = "3_Assessment.Rmd"}
```

```{r child = "4_HarvestProjections.Rmd"}
```

```{r child = "5_RegionalManagement.Rmd"}
```

```{r child = "6_ResearchNeeds.Rmd"}
```

```{r child = "7_Acknowledgments.Rmd"}
```
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thetable}{\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}
\newpage
```{r child = "8_Tables.Rmd"}
```
\newpage
```{r child = "9_Figures.Rmd"}
```
\newpage
```{r child = "10_References.Rmd"}
```

<div id="refs"></div>

\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thetable}{\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}
\newpage

```{r child = "11_Appendix_1.Rmd"}
```

```{r child = "12_Appendix_2.Rmd"}
```

```{r child = "13_Appendix_3.Rmd"}
```

```{r child = "14_Appendix_4.Rmd"}
```

<!-- ********************END OF THE DOCUMENT******************************* -->
